Cover letter for the original IJRR submission

### 2017-10-09 body/equilibrium.tex
[review] Minor

% !TEX root =  ../main.tex

@@

We observe that if $b_0$ is positive then \eqref{eq:lin_prog} admits a solution, and $b_0$ is proportional to the minimum distance of the contact forces to the boundaries of the friction cones.
If $b_0$ is negative, the configuration is not in static equilibrium, and $b_0$ indicates ``how far'' from equilibrium the configuration is. We thus use $b_0$ as a measure of robustness.
%~ One advantage of $b_0$ is that it gives a constant margin 
A simple approach to robustness consists in choosing a smaller friction coefficient, to constrain the forces to lie away from the boundaries of the real cone.  However, this would result in a small safety margin for forces of low magnitude, and an excessively big safety margin for large forces as the boundaries grow more and more appart. In comparison, our margin $b_0$ is constant, and provides a helpful mean to compare the robustness of different contact configurations.

>>>>

% !TEX root =  ../main_tro.tex

@@

We observe that if $b_0$ is positive then \eqref{eq:lin_prog} admits a solution, and $b_0$ is proportional to the minimum distance of the contact forces to the boundaries of the friction cones.
If $b_0$ is negative, the configuration is not in static equilibrium, and $b_0$ indicates ``how far'' from equilibrium the configuration is. We thus use $b_0$ as a measure of robustness.
%~ One advantage of $b_0$ is that it gives a constant margin 
A simple approach to robustness consists in choosing a smaller friction coefficient, to constrain the forces to lie away from the boundaries of the real cone.  However, this would result in a small safety margin for forces of low magnitude, and an excessively large safety margin for large forces as the boundaries grow more and more apart. In comparison, our margin $b_0$ is constant, and provides a helpful mean to compare the robustness of different contact configurations.
